\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Interview Summary}
\author{Michael Hanna - 40075977}
\date{}
\renewcommand{\baselinestretch}{1.15}

\usepackage{natbib}
\usepackage{graphicx}

\newenvironment{qanda}{\setlength{\parindent}{0pt}}{\bigskip}
\newcommand{\Q}{\bigskip\bfseries Q: }
\newcommand{\A}{\par\textbf{A:} \normalfont}
 

\begin{document}

\maketitle
\begin{qanda}
 
\Q What are the operators do you use in a calculator?
\A I use all the operators.

\Q What do you dislike about a calculator?
\A I don't like writing long equations in a calculator.

\Q  How often do you use a calculator?
\A I use a calculator every day for my physics problems.

\Q  Do you like to use your mind to do the calculation or to use a calculator?
\A It depends, if the calculation is easy, then I would use my mind, however, if the number is more than 4 digits, then I would use a calculator.

\Q What constants do you want to have in a calculator?
\A I would like the calculator to have all possible constants since I like to have precise calculations for my experiments. for example: Pi,e,...

\Q Do you prefer a console or GUI calculator?
\A I would prefer to use MATLAB. 

\Q What are the functions do you wish to have in a calculator and didn't you find it yet?
\A Custom log base, Usually in calculators, you can only do ln and log, But log to the base 3 is not available.

\Q Have you ever had a bad experience with a calculator?
\A Accidentally, I pressed the erase button, so I needed to re-enter everything again.

\Q Do you like a calculator to plot a graph?
\A Yes

\Q do you prefer a real or soft calculator?
\A A real one, It's easy to carry it.

\Q Have you ever heard about the plastic number?
\A Yes.

\Q what is the application for that number?
\A it is used in Geometry; it can be used to partition a square into three rectangles.

\Q Finally, what are your recommendations?
\A I would recommend having a calculator with a large display, and it can plot a graph.

\end{qanda}

\end{document}
